\textls[-0]{\thetitle}

### 2023-03-31 metatheory2.tex
Typo.

Indeed, for MLTT, we only have syntactic term and their judgemental equality (conversion rules) between them. However, we still can have \emph{an interpreter} about our MLTT in our ambient meta-logic. For a programmer, this is just like writting a Haskell meta-circular interpreter~\cite{abelson1996structure} that interpret an abstract syntax tree into Haskell's data structure. For a logician, this is just interpreting the syntactic $\goodTerm{\cdot}{t}{\cB}$ to an element $t \in \{\true, \false \}$. For a formal semanticist, this can be considered as a naive form of denotational semantic.

This interpreter is in the form of our canonicity theorem~\cref{thm:canonicity} in the light of Curry-Howard Correspondence, as any closed program of type $\cB$ is evaluated to either $\true$ or $\false$ under this theorem.
What's more, our canonicity theorem not only return the evaluation result, but also \emph{reflects} this computational traces into MLTT as a proof term of the derivation $t \equiv \true$ or $t \equiv \false$.

>>>>

Indeed, for MLTT, we only have syntactic term and their judgemental equality (conversion rules) among them. However, we still can have \emph{an interpreter} about our MLTT in our ambient meta-logic. For a programmer, this is just like writting a Haskell meta-circular interpreter~\cite{abelson1996structure} that interpret an abstract syntax tree into Haskell's data structure. For a logician, this is just interpreting the syntactic $\goodTerm{\cdot}{t}{\cB}$ to an element $t \in \{\true, \false \}$. For a formal semanticist, this can be considered as a naive form of denotational semantic.

This interpreter is in the form of our canonicity theorem~\cref{thm:canonicity} in the light of Curry-Howard Correspondence, as any closed program of type $\cB$ is evaluated to either $\true$ or $\false$ under this theorem.
What's more, our canonicity theorem also \emph{reflects} this computational traces into MLTT as a proof term of the derivation $t \equiv \true$ or $t \equiv \false$. From this perspective, we can see the similarity between the unidirectional small-step relation and the bidirectional conversion rules.
